---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
library(bboudata)
```

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
[![R-CMD-check](https://github.com/poissonconsulting/bboudata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/bboudata/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/bboudata/branch/main/graph/badge.svg)](https://app.codecov.io/gh/poissonconsulting/bboudata?branch=main)
<!-- badges: end -->

# bboudata

`bboudata` provides sample survival and recruitment data for boreal caribou.

## Installation

You can install the latest version of `bboudata` from [GitHub](https://github.com/poissonconsulting/bboudata) with:

``` r
# install.packages("remotes")
remotes::install_github("poissonconsulting/bboudata")
```

## Demonstration

``` {r}
library(tibble) # to enhance readability

bboudata::bbourecruit_a

bboudata::bbousurv_a
```

## bbou Suite

`bboudata` is part of the bbou suite of tools. 
Other packages in this suite include:

- [bboutools](https://github.com/poissonconsulting/bboutools)
- [bbouretro](https://github.com/poissonconsulting/bbouretro)
- [bboushiny](https://github.com/poissonconsulting/bboushiny)
- [bbousims](https://github.com/poissonconsulting/bbousims)

## Contribution

Please report any [issues](https://github.com/poissonconsulting/bboudata/issues).

## Code of Conduct

Please note that the bboudata project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). 
By contributing to this project, you agree to abide by its terms.

```{r, results = "asis", echo = FALSE}
cat(bboudata::licensing_md())
```
