---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/poissonconsulting/bboudata/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/poissonconsulting/bboudata/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

# bboudata

`bboudata` provides sample survival and recruitment data for boreal caribou.

## Installation

You can install the development version of bboudata from [GitHub](https://github.com/poissonconsulting/bboudata) with:

``` r
# install.packages("devtools")
devtools::install_github("poissonconsulting/bboudata")
```

## Demonstration

``` {r}
library(tibble) # to enhance readability

bboudata::bbourecruit_a

bboudata::bbousurv_a
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/bboudata/issues).

[Pull requests](https://github.com/poissonconsulting/bboudata/pulls) are always welcome.

## Code of Conduct

Please note that the bboudata project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
